\Title

### 2023-06-14 Grimaldi-etal-BiolCybernetics.tex
correc Miles: Methods

In this paper, we test whether the HD-SNN model is able to efficiently learn to solve a motion detection task defined by a realistic event-based data stream. This type of signal is commonly captured by a Dynamic Vision Sensor (DVS) and is inspired by the signal sent from the retinal ganglion cells through the optic nerve to the visual cortex. The events are binary in nature and should be sufficient to perform the motion detection task in a fast and efficient manner. Here we first describe the task definition and then the HD-SNN model we use for motion inference and how we train it.

>>>>

In this paper, we test whether the HD-SNN model is able to efficiently learn to solve a motion detection task defined by a realistic event-based data stream. This type of signal is commonly captured by an event-based camera, or Dynamic Vision Sensor (DVS) and is inspired by the signal sent from the retinal ganglion cells through the optic nerve to the visual cortex. The events are binary in nature and should be sufficient to perform the motion detection task in a fast and efficient manner. Here we first describe the task definition and then the HD-SNN model we use for motion inference and how we train it.
